---
title: "HW 02"
author: "INSERT YOUR NAME HERE"
format: 
  html:
    embed-resources: true
toc: true
---

## 1 - A new day, a new plot, a new geom

```{r}
#| label: label-me-1
options(warn=-1)
if (!require("pacman")) 
  install.packages("pacman")

# use this line for installing/loading
pacman::p_load(tidyverse,
               glue,
               scales,
               openintro,
               gridExtra,
               ggrepel,
               ggmap,
               ggridges,
               dsbox,
               devtools,
               fs,
               janitor) 
```

**A new day, a new plot, a new geom.** The goal of this exercise is to learn about a new type of plot (ridgeline plot) and to learn how to make it.

Use the `geom_density_ridges()` function from the **ggridges** package to make a ridge plot of of Airbnb review scores of Edinburgh neighborhoods. *The neighborhoods should be ordered by their median review scores.* The data can be found in the **dsbox** package, and it’s called `edibnb`. *Also include an interpretation for your visualization.* You should review feedback from your Homework 1 to make sure you capture anything you may have missed previously.

*(Note:* This is not a geom we introduced in class, so seeing an example of it in action will be helpful. Read the package README at <https://wilkelab.org/ggridges> and/or the introduction vignette at <https://wilkelab.org/ggridges/articles/introduction.html>. There is more information than you need for this question in the vignette; the first section on Geoms should be sufficient to help you get started.)

```{r}
devtools::install_github("tidyverse/dsbox")
library(dsbox)
my_edibnb_data <- edibnb
```

```{r}
library(ggplot2)
library(ggridges)

ggplot(my_edibnb_data %>% filter(!is.na(review_scores_rating)), 
       aes(x = review_scores_rating, 
           y = fct_reorder(neighbourhood, 
                           review_scores_rating, .fun = median), 
           fill = neighbourhood)) +
  geom_density_ridges() +
  xlim(75, 105) +
  labs(title = "Edinburgh - Ridge Plot",
      x = "Review Score Rating",
      y = "Neighbourhood")
# Observations:

# The plot above showing the ridge lines per neighborhoods in the city of Scotland, shows that all of the neighborhoods have very similar ratings, centered at ~95. All of the neighborhoods have a small hump at 80, and then they increase, until they reach 100. Based on the data, I would think that we should get a very good experience renting a house in Edinburgh.
```

```{r}
# get a list of files with "Foreign Connected PAC" in their names
list_of_files <- dir_ls(path = "data", regexp = "Foreign Connected PAC")

# read all files and row bind them
# keeping track of the file name in a new column called year
pac <- read_csv(list_of_files, id = "year")
```

```{r}
pac <- pac |>
  separate(year, into = c("source", "year_2"), sep = "-")


```

```{r}
pac$year_2 <- gsub("\\.csv$", "", pac$year_2)
```

```         
```

## 3 - Median housing prices in the US

## 4 - Expect More. Plot More.

## 5 - Mirror, mirror on the wall, who’s the ugliest of them all?
